A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-08-26 README.Rmd
change links for badges

This is the accompanying GitHub repository to a work in progress paper by Aaron Peikert[![ORCID iD](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7813-818X) and Andreas Brandmaier [![ORCID iD](https://orcid.org/sites/default/files/images/orcid_16x16.png)](http://orcid.org/0000-0001-8765-6982). [![licensebuttons by](https://licensebuttons.net/l/by/3.0/88x31.png)](https://creativecommons.org/licenses/by/4.0)

>>>>

This is the accompanying GitHub repository to a work in progress paper by Aaron Peikert[![ORCID iD](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7813-818X) and Andreas Brandmaier [![ORCID iD](https://orcid.org/sites/default/files/images/orcid_16x16.png)](http://orcid.org/0000-0001-8765-6982).

[![licensebuttons by](https://licensebuttons.net/l/by/3.0/88x31.png)](https://creativecommons.org/licenses/by/4.0) [![Ask Me Anything !](https://img.shields.io/badge/Ask%20me-anything-1abc9c.svg)](https://github.com/aaronpeikert/reproducible-research/issues/new) ![Open Source Love](https://badges.frapsoft.com/os/v2/open-source.svg?v=103)
